---
title: "Simple document"# 哦哦所以这不是一个R文件，这个是一个能run但也有不能run部分的markdown file teaching?
author: "Who"
output: 
html_document     ##here can also be pdf_document:true   then click the knit,then u can get the pdf doc
  toc：true
  toc_float:true
---

I'm an R Markdown document! 
#section 0
```{r echo=F, message= F}
library(tidyverse)
```


# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

#section 3:a tibble
```{r}
set.seed(1)
plot_df= tibble(
    x=rnorm(1000, sd=0.5),
    y= 1+2*x+rnorm(1000)
  )
```

#section 4
```{r，echo=F}

## histogram of x
ggplot(plot_df, aes(x = x)) + geom_histogram()

## scatterplot of x and y
ggplot(plot_df, aes(x = x, y = y)) + geom_point()
```
#section5 assemssment 2
This plot show the distribution of the absolute value of $X
```{r}
set.seed(0)
la_df=tibble(
  num_var=rnorm(n=500,mean=1),
  log_var=num_var>0,
  abs_var=abs(num_var)
  
)
ggplot(la_df,aes(x=abs_var))+geom_histogram()

```
The median is  `r round(median(pull
la_df,num_var)),2)`

##右上角那个符号到底是什么
##he clicked "render" below then he got thr html file? or should we click "visual"
#nono he clicked the "knit" over there, ohhhhh the thing u wanna get is the html focument which has been decided in the head of this template
#section 7 
Text formatting 



------------------------------------------------------------

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell

#learning assisnamnet 3
After the previous code chunk, write a bullet list given the mean, median, and standard deviation of the original random sample.

 *The median is :`r round(median(pull(la_df,num_var)),2)`.
 
 *The mean is : `r round(mean(pull(la_df,num_var)),2)`.



 
